---
title: "Unit 1 - 3 Review Starter"
author: "Insert your group number here"
date: "Insert date here"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 2

Remove this text, and add your answer for Exercise 2 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
